\documentclass[letterpaper,10pt]{article}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage{balance}
%\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}
\usepackage{pstricks, pst-node}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

%Allow sub titles
\usepackage{titling}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\def\name{Trevor Swope, David Okubo, and Megan McCormick}

%pull in the necessary preamble matter for pygments output
\input{pygments.tex}

%% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {cs444 ``operating systems'' files filesystem I/O},
  pdftitle = {CS 444 Homework 2 Write Up},
  pdfsubject = {CS 444 Homework 2},
  pdfpagemode = UseNone
}

%Set Up title page
\title{Project 2: I/O Elevators}
\subtitle{CS 444, Spring 2018}
\author{Trevor Swope, David Okubo, and Megan McCormick}
\begin{document}

%Create Title page
\begin{titlingpage}
\maketitle 
\begin{abstract}

\end{abstract}
\end{titlingpage}
\section{Questions}
\subsection{1. What do you think the main point of the assignment is?}
The main point of this assignment is probably to get us thinking about how the kernel handles requests for I/O of data from the disk, and understand the benefits of different schedulers. It was also a good introduction to kernel programming and understanding how to implement a patch to Linux.

\subsection{2. How did you personally approach the problem? Design decisions, algorithms, etc.}
After writing down pseudocode for both LOOK and C-LOOK, we decided to use C-LOOK; doing C-LOOK as opposed to LOOK allowed us to move the disk head only in one direction, simplifying the implementation somewhat.

\subsection{3. How did you ensure your solution was correct? Testing details, for instance.}
We put kprint statements in the dispatch and add functions; when a request is added, it is printed as either read or write, and when a request is dispatched, it is printed as either read or write. This way, we see that when requests are added, they are dispatched in the expected order.

\subsection{4. What did you learn?}
From tracing through the No-op scheduler code we obtained an extensive understanding of how schedulers work on a Linux kernel. After writing the C-Look scheduler, we discovered it to be very similar in code, but you can see how it is a more efficient scheduler.

\subsection{5. How should the TA evaluate your work? Provide detailed steps to prove correctness.}
We run qemu with the following flags after sourcing the environment:\\
qemu-system-i386 -gsb tcp::5516 -S -nographic -kernel /scratch/spring2018/16/linux-yocto-3.19-assignment\_2/arch/x86/boot/bzImage -drive file=core-image-lsb-sdk-qemux86.ext4 -enable-kvm -net none -usb -localtime --no-reboot --append "root=/dev/hda rw console=ttyS0 debug"\\
Then, we connect in a separate shell with:\\
gdb -tui\\
\$GDB\\
target remote:5516\\
Continue\\
Then, in the vm, you should see reads and writes happen as they start up. You should observe that requests that are dispatched in ascending order of disk position. For a simple test, run the following commands:\\
touch file\\
cat file\\
This should read and write.

\section{Version Control History}
\input{changelog.tex}

\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{hw2}

\end{document}
